The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 Results/analysis.tex
Edited through the results section

\subsection{Analysis of the received e-mail data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \texttt{bcc} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

	\item E-Mails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability which we would like to christen \texttt{To~header injection}. These injections reflect the ability to inject any number of e-mail addresses into the \texttt{to} field while being unable to inject any other header into the e-mails. We attribute this behavior to inconsistent sanitization by the application. 
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed e-mail addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over the e-mails sent, \texttt{To header injection} makes it possible to append any number of e-mail addresses, thereby enabling us to leak information, and/or perform DoS (Denial of Service) attacks.

	\item E-Mails with the \texttt{x-check} header successfully injected\\
    The third category of e-mails received were e-mails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    these let us differentiate between unsuccessful attempts and successful attempts by injecting the additional header, allowing us to check whether headers other than the \texttt{bcc} header can be injected into the generated e-mail. 
\end{enumerate}
We list each category and the number of e-mails received by the category in Table~\ref{tab:analysis}.

\input{Results/data_analysis}
We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	These represent the perfect attack scenario where we are able to inject multiple headers into the e-mails. We can see that over 70\% of the received \texttt{bcc} header injected e-mails are also susceptible to other header injections.

	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we are able to inject additional headers into the e-mail. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular E-Mail Header Injection.

	\item \texttt{x-check} headers found in \texttt{nuser} e-mails\\
	In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account. We explain the presence of these headers in the following paragraph.

	\item Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\\
	These represent the e-mails with \lstinline|form_ids| that were \emph{not} already found in the \texttt{maluser} account. We attribute these e-mails to (probably) having a backend that was built with Python or another language having a similar behavior with respect to constructing headers.

	\item Total successful injections\\
	This represents the total number of successful injections our system made. This includes the E-Mail Header Injections with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} e-mails\,(7). This is the total number of vulnerabilities that were found by our system.

>>>>

\subsection{Analysis of the Received \Email Data}
During our analysis of the received \emails, we found that the \emails that we received belonged to one of three categories:
\begin{enumerate}
	\item \Emails with the \texttt{bcc} header successfully injected\\
	  This form of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command?
      265 such \emails in our received \emails. This validates that the web applications that sent these \emails are vulnerable to \ehi.

	\item \Emails with the \texttt{to} header successfully injected\\
	We discovered an unintended vulnerability class during our analysis, which we call \texttt{To~header injection}. These injections reflect the ability to inject any number of \email addresses into the \texttt{to} field of the SMTP message while being unable to inject any other header into the \emails. We attribute this behavior to inconsistent sanitization by the application. 
    % Adam: I can't understand what this sentence is trying to say
	The vulnerability is further aided by the leniency shown by mail servers, wherein they parsed malformed \email addresses and delivered it to the right mail server, and on the receiving end, the mail was delivered to the right mailbox.

	While not allowing us complete control over content of the \emails sent, \texttt{To header injection} makes it possible to append any number of \email addresses, thereby enabling us to leak information or perform DoS (Denial of Service) attacks against the web application.

	\item \Emails with the \texttt{x-check} header successfully injected\\
    The third category of \emails received were \emails with the \texttt{x-check} header injected. As discussed in Section~\ref{analyze:detect_x_check}, 
    we can differentiate between unsuccessful attempts and successful attempts by injecting the additional header and checking whether headers other than the \texttt{bcc} header can be injected into the generated \email. 
\end{enumerate}

% Adam: Sai, we need to put the actual numbers in the text. We cannot count on the readers to look at the table (of course, we should use the commands
We list each category and the number of \emails received by the category in Table~\ref{tab:analysis}.

\input{Results/data_analysis}

We explain the combination of these header injections (4-7) as follows:
\begin{itemize}
	\item \Email Header Injections with \texttt{bcc} and \texttt{x-check} headers\\
	  These represent the scenario where an attacker can inject multiple headers into the \emails. We can see that over 70\% of the received \texttt{bcc} header injected \emails are also susceptible to other header injections.
      % Adam: What is the exact percentage? We should use that rather than an approximate number

	\item Both \texttt{To} header injections and \texttt{x-check} headers \\
	This combination shows us that in addition to being able to inject into the \texttt{To} fields, we injected additional headers into the \email. It is not clear what causes this behavior; however, these can be exploited to achieve the same result as a regular \ehi.

	\item \texttt{x-check} headers found in \texttt{nuser} \emails\\
	  In addition to analyzing the \texttt{maluser} account, we also analyze emails received by the \texttt{nuser} account.
      % Adam: Why aren't we explaining this here? It reads strange.
      We explain the presence of these headers in the following paragraph.

	\item Unique \texttt{x-check} headers found in \texttt{nuser} \emails\\
	  These represent the \emails with unique form ids that were \emph{not} already found in the \texttt{maluser} account. We attribute these \emails to (probably) having a web application that was built with Python or another language having a similar behavior with respect to constructing headers.
      % Adam: What is the actual behavior? This is confusing.

	\item Total successful injections\\
	  This represents the total number of successful injections. This includes the \ehi with \texttt{bcc} header\,(1), \texttt{To} header injections alone\,(3), and Unique \texttt{x-check} headers found in \texttt{nuser} \emails\,(7). This is the total number of vulnerabilities that were found by our system.

      % Adam: we need the actual #s here too. These are the core results of our analysis, they need to be in the text.

### 2016-05-23 Results/disclosure.tex
texts
final data update
Edited through the results section

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we had discovered E-Mail Header Injection vulnerability on a particular website, we e-mailed the developers of these vulnerable websites disclosing the pages that contained the vulnerability, along with a brief description of the vulnerability.
We chose to e-mail the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
\begin{itemize}
	\item security@domain.com - Used for Security bulletins or queries.
	\item admin@domain.com - Used to contact the administrator of a website.
	\item webmaster@domain.com - Synonym for administrator, same functionality as admin.
\end{itemize}

Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails. For the remaining domains, we used the \dq{\texttt{whois}}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.

We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \dq{lower bound} for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated. We discuss this possibility, and other concepts such as limitations and methods for mitigation of the vulnerability in the following section.

>>>>

\subsection{Responsible Disclosure of Discovered Vulnerabilities}
After we discovered an \ehi vulnerability on a particular website, we attempted to notify the developers of the vulnerable web application, along with a brief description of the vulnerability.
We chose to \email the following mailboxes, following the rules specified in RFC~2142~\cite{rfc2142}:
% Adam: don't we use \texttt for all the email addresses in the paper? We should use the same thing here
\begin{itemize}
	\item security@domain.com - Used for Security bulletins or queries.
	\item admin@domain.com - Used to contact the administrator of a website.
	\item webmaster@domain.com - Synonym for administrator, same functionality as admin.
\end{itemize}

% Adam: sai, is this number up-to-date? 
Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes able to receive \emails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to find the contact details of the owner, then we \emailed. The number of emails we sent and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}[tbp]
\centering
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{Notified websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	\domains\ & 13 & 9 \\
	\hline
\end{tabular}
	\caption[\titlecap{}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}

% Adam: did we get updated notifications?
We received 13 developer responses, confirming 9 discovered vulnerabilities. Two of the developers fixed the vulnerability on their website.
% is this done?
From our research, it is clear that \ehi is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a \emph{lower bound} for prevalence of \ehi vulnerability, and can quite easily be larger if the attacks were broader, crafted for the individual web application, and  less automated.

### 2016-05-23 Results/fuzz_result.tex
chap5 added
Edited through the results section

\section{Fuzzed data}
We performed our fuzzing attempts on the gathered data with both the regular payload and malicious payload. Table~\ref{tab:fuzzed_data} shows the quantity of e-mails that we received for each payload. We explain in detail what each piece of data shown in the table represents, in the following sections.
\input{Results/fuzzed_data}
\paragraph{E-Mail received from forms}
The e-mails that we received can be broadly categorized into two categories:
\begin{enumerate}
	\item E-Mails due to regular payload\\
	This represents the total number of websites that sent e-mails to us. This indicates that we were able to successfully submit the forms on these sites.

	\item E-Mails due to malicious payload\\
    Once we receive an e-mail from a website due to the regular payload, we go back and fuzz those forms with more malicious payloads. This field, in essence, represents the total number of unique URLs that contain E-Mail Header Injection vulnerability.
\end{enumerate}

>>>>

\subsection{Fuzzed Data}
Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
\input{Results/fuzzed_data}
\paragraph{\Email received from forms}
The \emails that we received can be categorized into two categories:
\begin{enumerate}
	\item \Emails due to regular payload\\
	This represents the total number of web applications that sent \emails to us. This indicates that we were able to successfully submit the forms on these sites to trigger the web application to send an \email.

	\item \Emails due to malicious payload\\
    Once we receive an \email from a web application due to the regular payload, we fuzz those forms with the malicious payloads. This field represents the total number of unique URLs that are  contain an \ehi vulnerability.
\end{enumerate}

### 2016-05-23 Results/pipeline.tex
Edited through the results section

\subsection[The Pipeline]{Understanding the pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

At each stage of the pipeline, the amount of data trickles down, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found. Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.

@@

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.

>>>>

\subsection[The Pipeline]{Understanding the Pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

At each stage of the pipeline, the amount of data decreases, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found. Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.

@@

% Adam: this is an important part of our contribution, but I don't think that it belongs here. 
%% From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.

### 2016-05-23 Results/pre_result.tex
chap5 added
Edited through the results section

\section{Collected Data}
From our extensive crawl of the web, we were able to gather the data shown in Table~\ref{tab:data}. The following paragraphs describe in detail what each kind of data represents, and what they signify.

@@

\paragraph{URL's crawled}
This represents the total number of unique URLs that we crawled on the World Wide Web. It is to be noted that this quantity refers to unique URL's, and not websites.

\paragraph{Total Forms found}
This represents the total number of forms that were found on the URL's crawled. We found a total of \forms\ forms from 
\uniqueforms\ unique domains.

\paragraph{Forms with E-Mail Fields}
This represents the total number of forms that were found to contain e-mail fields. We found \emailforms\ such forms from \uniqueemailforms\ unique domains.

>>>>

\subsection{Collected Data}

% TODO: Need to put in a number here, and discuss the high level
% crawl. 
We ran the system for XYZ days/hours/whatever

From our extensive crawl of the web, we were able to gather the data
shown in Table~\ref{tab:data}. Our system crawled \urls unique URLs,
found a total of \forms\ forms from \uniqueforms\ unique domains, and
found \emailforms\ forms that contained an \email field from \uniqueemailforms\ unique domains.

@@
